\documentclass{article}

\usepackage{parskip}
\usepackage{titling}
\usepackage[backend=bibtex,
style=numeric
]{biblatex}
\addbibresource{bibliography}

% Document metadata
\title{
    GEOG 5561 Term Project: Revision Memo
}
\author{
    Aamdal, Haakon\\
    \texttt{aamda001@umn.edu}
}


% Margins
% Margins
\topmargin=-0.45in
\evensidemargin=0in
\oddsidemargin=0in
\textwidth=6.5in
\textheight=9.5in
\headsep=0.25in
\begin{document}
\maketitle
\section{Comments and suggestions from my peers}
\label{sec:Comments and suggestions from my peers}
The following points lists the feedback I've received on my draft:
\begin{enumerate}
  \item Discard the businesses, focus only on households.
  \item Skip the conclusion, it's not needed.
  \item Use median income instead of average income.
  \item Use census blocks instead of tracts.
  \item Elaborate on how internet speed in the area will affect profitability.
  \item Add something about whether the GIS analyst will receive training or not.
  \item Question about whether my system will have the ability to monitor trends over time and make predicitions about the future demand and profitability.
  \item Countless gramatical and structural errors.
\end{enumerate}

\section{Changes for the final paper}
\label{sec:Changes for the final paper}
Since our group met for the review so close to this memo's deadline, none of the proposed changes have been incorporated yet. For my final paper, I plan to:
\begin{enumerate}
  \item Discard everything that has to do with businesses as potential customers. There are more than enough to write about when it comes to households only.
  \item Remove the conclusion.
  \item Look closer into the Census data. I might by mistake have written average income instead of median income, so I need to look closer into the datasets provided by the census. At the same time, I will have to get a better overview over the different definitions of blocks/tracts.
  \item Add a paragraph where I explain why the ISP should prefer areas with low internet speeds and poor technology. There's already some text about this, but since I've got numerous questions about this, it's obviously not precise enough.
  \item I will not add information about whether the analyst will receive training or not, but perhaps add a little more on how to operate the system, so the paper can be used as a reference manual for the analyst.
  \item Point 7 is out of the scope of this paper, so it will be discarded.
\item Thanks to Spencer, I have a printout of my paper full of red pen strokes. I'll go over all the comments and corrections to make sure my paragraphs are better structured and gramatically correct.
\end{enumerate}


\end{document}
